---
title: "MITUS -- Aging Pt 5"
geometry: margin=2cm
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---


# New Weighted Mortality Calculations

The population data supplied is from mortality.org, the reference that Josh suggested on Tuesday. This source did have the single year population counts all the way to 1950. I used these and the single year mortality counts to create the new weighted mortality rates. Below are a series of plots that show the difference in the annual mortality rates from the original national model and these newly weighted rates. Every age band has been accounted for. 


#Pre-Optimization Performance  
##Model 1 --demographic version 
This simulation has the aging rates fit with a basic smoothed curve and the newly calculated weighted mortality rates.

```{r,message=FALSE, warning=FALSE, fig.width=4}
library(MITUS)
model_load("US")
prms <-list()
prms <- param(P)
IP <- list()
IP <- param_init(P)
#read in the population distribution data (file name is misnomer, to be updated)
popdist<- as.matrix(readRDS(system.file("US/US_PopCountsByAge.rds", package="MITUS")))
  popdist<-popdist[,-1]
rownames(popdist)<-as.matrix(readRDS(system.file("US/US_PopCountsByAge.rds", package="MITUS"))[,1])

#calculate the percentage of the total age band in each single year age 
ltd<-matrix(NA,10,69)

ltd[1,]<-popdist[5,]/colSums(popdist[1:5,])
ltd[2,]<-popdist[15,]/colSums(popdist[6:15,])
ltd[3,]<-popdist[25,]/colSums(popdist[16:25,])
ltd[4,]<-popdist[35,]/colSums(popdist[26:35,])
ltd[5,]<-popdist[45,]/colSums(popdist[36:45,])
ltd[6,]<-popdist[55,]/colSums(popdist[46:55,])
ltd[7,]<-popdist[65,]/colSums(popdist[56:65,])
ltd[8,]<-popdist[75,]/colSums(popdist[66:75,])
ltd[9,]<-popdist[85,]/colSums(popdist[76:85,])
ltd[10,]<-popdist[95,]/colSums(popdist[86:95,])


#invert this for the aging rate
ltd<-1/ltd

td<-matrix(NA,10,1201)
for (i in 1:10){
td[i,1:817]<-SmoCurve(as.numeric(ltd[i,]))
td[i,818:1201]<-td[i,817]
}

#plot the spline denominators
for(i in 1:10){
plot(t(td)[1:817,i], type="l")}

spl_den<-t(td)*12

##run the model with this denominator 
   zz<-list()
    zz <- cSim_demo_ag(nYrs       = 2018-1950         ,
                      nRes      = 24                  ,
                      InitPop  = prms[["InitPop" ]]   ,
                      Birthst  = prms[["Birthst"]]    ,
                      ImmNon    = prms[["ImmNon"]]   ,
                      ImmLat   = prms[["ImmLat" ]]  ,
                      ImmAct  = prms[["ImmAct"]]  ,
                      ImmFst   = prms[["ImmFst" ]]   ,
                      mubt       = prms[["mubt"]],
                      ag_den = spl_den)
         M <- zz$Outputs
      colnames(M) <- c(prms$ResNam[1:13],prms$ResNam[121:131]);
      df<-as.data.frame(M)
      #plot the results
      tb_graph_demomod(df)
```

##Model 2 --full model 
Everything as above, but the full model without optimization.

```{r,echo=FALSE, message=FALSE, warning=FALSE, fig.width=4}
library(MITUS)
model_load("US")
prms <-list()
prms <- param(P)
IP <- list()
IP <- param_init(P)
#read in the population distribution data (file name is misnomer, to be updated)
popdist<- as.matrix(readRDS(system.file("US/US_PopCountsByAge.rds", package="MITUS")))
popdist<-popdist[,-1]
rownames(popdist)<-as.matrix(readRDS(system.file("US/US_PopCountsByAge.rds", package="MITUS"))[,1])

#calculate the percentage of the total age band in each single year age 
ltd<-matrix(NA,10,69)

ltd[1,]<-popdist[5,]/colSums(popdist[1:5,])
ltd[2,]<-popdist[15,]/colSums(popdist[6:15,])
ltd[3,]<-popdist[25,]/colSums(popdist[16:25,])
ltd[4,]<-popdist[35,]/colSums(popdist[26:35,])
ltd[5,]<-popdist[45,]/colSums(popdist[36:45,])
ltd[6,]<-popdist[55,]/colSums(popdist[46:55,])
ltd[7,]<-popdist[65,]/colSums(popdist[56:65,])
ltd[8,]<-popdist[75,]/colSums(popdist[66:75,])
ltd[9,]<-popdist[85,]/colSums(popdist[76:85,])
ltd[10,]<-popdist[95,]/colSums(popdist[86:95,])


#invert this for the aging rate
ltd<-1/ltd

td<-matrix(NA,10,1201)
for (i in 1:10){
td[i,1:817]<-SmoCurve(as.numeric(ltd[i,]))
td[i,818:1201]<-td[i,817]
}

spl_den<-t(td)*12

trans_mat_tot_ages<<-reblncd(mubt = prms$mubt,can_go = can_go,RRmuHR = prms$RRmuHR[2], RRmuRF = prms$RRmuRF, HRdist = HRdist, dist_gen_v=dist_gen_v, adj_fact=prms[["adj_fact"]])
  zz <- cSim_ag(  nYrs       = 2018-1950         , nRes      = length(prms[["ResNam"]])  , rDxt     = prms[["rDxt"]]  , TxQualt    = prms[["TxQualt"]]   , InitPop  = prms[["InitPop"]],
               Mpfast     = prms[["Mpfast"]]    , ExogInf   = prms[["ExogInf"]]       , MpfastPI = prms[["MpfastPI"]], Mrslow     = prms[["Mrslow"]]    , rrSlowFB = prms[["rrSlowFB"]]  ,
               rfast      = prms[["rfast"]]     , RRcurDef  = prms[["RRcurDef"]]      , rSlfCur  = prms[["rSlfCur"]] , p_HR       = prms[["p_HR"]]      , dist_gen = prms[["dist_gen"]]    ,
               vTMort     = prms[["vTMort"]]    , RRmuRF    = prms[["RRmuRF"]]        , RRmuHR   = prms[["RRmuHR"]]  , Birthst  = prms[["Birthst"]]    ,
               HrEntEx    = prms[["HrEntEx"]]   , ImmNon    = prms[["ImmNon"]]        , ImmLat   = prms[["ImmLat" ]] , ImmAct     = prms[["ImmAct"]]    , ImmFst   = prms[["ImmFst" ]]    ,
               net_mig_usb = prms[["net_mig_usb"]], net_mig_nusb = prms[["net_mig_nusb"]],
               mubt       = prms[["mubt"]]    , RelInf    = prms[["RelInf"]]        , RelInfRg = prms[["RelInfRg"]], Vmix       = prms[["Vmix"]]      , rEmmigFB = prms [["rEmmigFB"]]  ,
               TxVec      = prms[["TxVec"]]     , TunTxMort = prms[["TunTxMort"]]     , rDeft    = prms[["rDeft"]]   , pReTx      = prms[["pReTx"]]     , LtTxPar  = prms[["LtTxPar"]]    ,
               LtDxPar    = prms[["LtDxPar"]]   , rLtScrt   = prms[["rLtScrt"]]       , RRdxAge  = prms[["RRdxAge"]] , rRecov     = prms[["rRecov"]]    , pImmScen = prms[["pImmScen"]]   ,
               EarlyTrend = prms[["EarlyTrend"]], ag_den=spl_den, NixTrans = IP[["NixTrans"]],   trans_mat_tot_ages = trans_mat_tot_ages)
M <- zz$Outputs
colnames(M) <- prms[["ResNam"]]
df<-as.data.frame(M)
tb_graph_demo(df,FALSE)
```

#Post Optimization 
##Model 3 -- full model post optimization 

```{r,echo=FALSE, message=FALSE, warning=FALSE, fig.width=4}
library(MITUS)
model_load("US")
#load in the optimization dataset 
Opt <- readRDS("~/MITUS/inst/US/US_Optim_all_10_620.rds")
#set the Par 
Par<-Opt[8,-61]
#format the parameters 
# normal to uniform
Par2 <- pnorm(Par,0,1)
# uniform to true
Par3 <- Par2
Par3[idZ0] <- qbeta( Par2[idZ0], shape1  = ParamInitZ[idZ0,6], shape2 = ParamInitZ[idZ0,7])
Par3[idZ1] <- qgamma(Par2[idZ1], shape   = ParamInitZ[idZ1,6], rate   = ParamInitZ[idZ1,7])
Par3[idZ2] <- qnorm( Par2[idZ2], mean    = ParamInitZ[idZ2,6], sd     = ParamInitZ[idZ2,7])
P[ii] <- Par3
P <- P
prms <-list()
prms <- param(P)
IP <- list()
IP <- param_init(P)
#read in the population distribution data (file name is misnomer, to be updated)
popdist<- as.matrix(readRDS(system.file("US/US_PopCountsByAge.rds", package="MITUS")))
popdist<-popdist[,-1]
rownames(popdist)<-as.matrix(readRDS(system.file("US/US_PopCountsByAge.rds", package="MITUS"))[,1])

#calculate the percentage of the total age band in each single year age 
ltd<-matrix(NA,10,69)

ltd[1,]<-popdist[5,]/colSums(popdist[1:5,])
ltd[2,]<-popdist[15,]/colSums(popdist[6:15,])
ltd[3,]<-popdist[25,]/colSums(popdist[16:25,])
ltd[4,]<-popdist[35,]/colSums(popdist[26:35,])
ltd[5,]<-popdist[45,]/colSums(popdist[36:45,])
ltd[6,]<-popdist[55,]/colSums(popdist[46:55,])
ltd[7,]<-popdist[65,]/colSums(popdist[56:65,])
ltd[8,]<-popdist[75,]/colSums(popdist[66:75,])
ltd[9,]<-popdist[85,]/colSums(popdist[76:85,])
ltd[10,]<-popdist[95,]/colSums(popdist[86:95,])


#invert this for the aging rate
ltd<-1/ltd

td<-matrix(NA,10,1201)
for (i in 1:10){
td[i,1:817]<-SmoCurve(as.numeric(ltd[i,]))
td[i,818:1201]<-td[i,817]
}

spl_den<-t(td)*12

trans_mat_tot_ages<<-reblncd(mubt = prms$mubt,can_go = can_go,RRmuHR = prms$RRmuHR[2], RRmuRF = prms$RRmuRF, HRdist = HRdist, dist_gen_v=dist_gen_v, adj_fact=prms[["adj_fact"]])
  zz <- cSim_ag(  nYrs       = 2018-1950         , nRes      = length(prms[["ResNam"]])  , rDxt     = prms[["rDxt"]]  , TxQualt    = prms[["TxQualt"]]   , InitPop  = prms[["InitPop"]],
               Mpfast     = prms[["Mpfast"]]    , ExogInf   = prms[["ExogInf"]]       , MpfastPI = prms[["MpfastPI"]], Mrslow     = prms[["Mrslow"]]    , rrSlowFB = prms[["rrSlowFB"]]  ,
               rfast      = prms[["rfast"]]     , RRcurDef  = prms[["RRcurDef"]]      , rSlfCur  = prms[["rSlfCur"]] , p_HR       = prms[["p_HR"]]      , dist_gen = prms[["dist_gen"]]    ,
               vTMort     = prms[["vTMort"]]    , RRmuRF    = prms[["RRmuRF"]]        , RRmuHR   = prms[["RRmuHR"]]  , Birthst  = prms[["Birthst"]]    ,
               HrEntEx    = prms[["HrEntEx"]]   , ImmNon    = prms[["ImmNon"]]        , ImmLat   = prms[["ImmLat" ]] , ImmAct     = prms[["ImmAct"]]    , ImmFst   = prms[["ImmFst" ]]    ,
               net_mig_usb = prms[["net_mig_usb"]], net_mig_nusb = prms[["net_mig_nusb"]],
               mubt       = prms[["mubt"]]    , RelInf    = prms[["RelInf"]]        , RelInfRg = prms[["RelInfRg"]], Vmix       = prms[["Vmix"]]      , rEmmigFB = prms [["rEmmigFB"]]  ,
               TxVec      = prms[["TxVec"]]     , TunTxMort = prms[["TunTxMort"]]     , rDeft    = prms[["rDeft"]]   , pReTx      = prms[["pReTx"]]     , LtTxPar  = prms[["LtTxPar"]]    ,
               LtDxPar    = prms[["LtDxPar"]]   , rLtScrt   = prms[["rLtScrt"]]       , RRdxAge  = prms[["RRdxAge"]] , rRecov     = prms[["rRecov"]]    , pImmScen = prms[["pImmScen"]]   ,
               EarlyTrend = prms[["EarlyTrend"]], ag_den=spl_den, NixTrans = IP[["NixTrans"]],   trans_mat_tot_ages = trans_mat_tot_ages)
M <- zz$Outputs
colnames(M) <- prms[["ResNam"]]
df<-as.data.frame(M)
tb_graph_demo(df,FALSE)
```

#Next Steps
  * Approve these optims
  * regenerate pre-defined scenarios for US 
  * attempt to optimize the top 10 states with these national values 
  * combine program change model version with updated model with new aging denominators 
