---
title: "Optimizing Parameters for MITUS"
author: "Nicole A. B. Swartwood"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
Before beginning calibration of your model built in MITUS, it is critical to optimize the parameter inputs. Below is a description of the workflow for optimization of your model using the functions provided in the MITUS package. 

The first step in the optimization process is to generate a n sets of starting values. MITUS package has a function that will generate these values. The function "gen_st_val" allows the user to generate these values using 1 of 2 methods: samp = "NORM" will generate n datasets using a random normal number generator & samp = "LHS" will utilize Latin Hypercube Sampling.  

```{r}
# Generate 20 starting value datasets using Latin Hypercube Sampling 
MITUS::gen_st_val(n = 20, samp = "LHS") 
```

This dataframe will be used in the optim_b function in order to call the optimization process. This function executes 8 optimization steps (7 multi-variate and a final univariate optimization)

```r
#initiate optimization loop for the third set of starting values
#(the third row of the dataframe generated from gen_st_val)
optim_b(3)
```

